\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Object Models Based on Deep Learning for Object Similarity and Multi-Armed Bandits for Robust Grasp Planning \versionline{4}

### 2015-09-03 ICRA2016/bandits_docs/includes/experiments.tex
First full version of the paper with committed adobe illustrator figures

\subsection{Dataset}
To study the convergence rate with orders of magnitude of previous grasp data we create a dataset of tens of thousands of 3D CAD models.
We aggregated data from the laser scanned datasets Amazon Picking Challenge~\cite{}, BigBIRD~\cite{}, KIT~\cite{}, and YCB~\cite{}, as well as the synthetic datasets 3DNet~\cite{wohlkinger20123dnet} and the SHREC 2014 large-scale retrieval dataset~\cite{}.
To preprocess the data for grasping we set the frame of reference for each object to the the principal components of the vertices of each mesh, set the object center-of-mass as the center of a bounding box around the reoriented vertices, removed unreferenced and invalid vertices, rescaled each synthetic mesh such that its smallest principal direction fit within a PR2 gripper, and converted the mesh to a signed distance field.
We reserved the YCB dataset as a test set, and used subsets of the remaining data to train hyperparameters and to seed the CCBPs for convergence experiments on the test dataset.

\subsection{System}
To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud services.
We used Google Cloud Storage (GCS) to store the mesh models and to sample and evaluate 250 grasps per object.
Each model is stored in .OBJ format and the average size is roughly 0.5MB.
We used Google Compute Engine to distribute trials of MAB algorithms across objects, reducing the runtime of our large-scale experiments.
Our master analysis script can launch up to 600 GCE single core instances, each running Ubuntu 12.04.
When an instance is launched, we mount DexNet via a persistent disk containing a particular set of objects and grasps.
Each instance pulls our latest code from Github, runs a single python experiment script configured in a YAML file, compresses the results in an output directory, and uploads the results to GCS.
After all instances complete, the master script turns off all instances, unmounts all disks, downloads the results from each instance, and sends the user a notification email.
The results can be optionally analyzed by the master script.

@@

Preliminary experiments suggest that using CCBPs with prior data from DexNet reduces the number of samples for MAB algorithms to converge to a grasp with high probablity of force closure $P_F$ under uncertainty in object pose, gripper pose, and friction coefficient.
~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
The plot compares Thompson sampling, a MAB algorithm, without correlations to Thompson sampling using the CCBP model of local grasp similiarity (no prior data).
We see that the CCBP model outperforms the uncorrelated model by approximately 10$\times$ for the cereal box but has comparable performance to Thompson sampling on the flower pot.
Iniitial reuslts suggest that performance on the flower pot is poorer because it has very few similar grasps according to our similarity metric.

\begin{figure}[t!]
\centering
	\begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.08]{figures/box_avg_reward_w_model.jpg}
        \caption{Normalized $P_F$ on a cereal box with 250 candidate grasps.}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.08]{figures/flowerpot_avg_reward_w_model.jpg}
        \caption{Normalized $P_F$ on a flower pot with 250 candidate grasps.}
    \end{subfigure}
\caption{Comparison of the normalized $P_F$ of the sampled grasp versus iteration of the MAB algorithm for correlated Thompson sampling, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials. (a) On the cereal box, correlated Thompson sampling converges to within 90\% of the highest quality grasp approximately 4$\times$ faster than uncorrelated. (b) However, correlated and uncorrelated Thompson sampling perform comparably on the flower pot because there are few grasp similarities in the candidate set. }
\figlabel{local-mab}
\vspace*{-15pt}
\end{figure}

To examine the effects of orders of magnitude of prior data in the MAB algorithms, we ran the algorithms with priors computed from increasingly larger subsets of prior data from DexNet: 0, 15, 150, and 1500 objects. 
\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for a bottle using prior grasp data from the five nearest neighbor objects in DexNet averaged over 50 trials.
Each other object was labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
We see that the convergence of the correlated MAB algorithms to a grasp with high $P_F$ accelerates with increasingly largers subsets of prior data used.
This suggests that adding more prior data may further accelerate convergence, because it is increasingly likely that a similar object and grasp exists in the dataset as the size increases.
Future work will examine these effects on a larger subset of objects and will use more than five nearest neighbors from DexNet to compute priors, which may lead to even larger gains for larger subsets of prior data.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model2.jpg}
\caption{Comparison of the normalized $P_F$ of the sampled grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from DexNet, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials on the bottle object. Prior grasps were taken from increasingly larger subsets of DexNet: 15, 150, and 1500 objects. We see that convergence to within 90\% of the optimal grasp is accelerated by approximately 10$\times$ over uncorrelated Thompson sampling, and performance appears to improve with increasing sizes of the prior dataset used. }
\figlabel{global-mab}
\vspace*{-15pt}
\end{figure}

\TODO{Remove below section}
We are currently working on an experiment to quantify the gains in convergence time across orders of magnitudes of prior data (10, 100, 1000, 10000) from DexNet using Google Compute Engine.
Our initial version will be run on a relatively small subset of test objects, and in the coming weeks we will average the performance over a larger set of test objects.
We are particularly interested in seeing if there is a point of diminshing returns from adding more data when using datasets on the order of 10,000 - 100,000 objects.
We are also interested in whether or not adding perturbations to the data such as object reflections and shape perturbations will also increase performance, as has been observed for training Deep CNNs in vision~\cite{krizhevsky2012imagenet}.

@@

>>>>

\TODO{All experiments here are preliminary. Add new results from non-symmetric objects and more data}
\TODO{Include experiments on sensitivity to uncertainty} \\
\TODO{Images of selected grasps} \\

We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity to parameters of the algorithm.
To test the generalization of our feature maps, we reserved objects from YCB and ModelNet as a test set, and used nested subsets of the remaining data as training data for optimizing the hyperparameters and for tuning the MAB convergence rate.
We assumed a PR2 gripper for our grasps, which has a maximum width of approximately $10cm$.
We assumed isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
The weights of our similarity kernel were selected using a grid search over possible values on a held-out validation set.

\subsection{System}
To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud services.
We used Google Cloud Storage (GCS) to store the mesh models and to sample and evaluate 250 grasps per object.
We used Google Compute Engine to distribute trials of MAB algorithms across objects, reducing the runtime of our large-scale experiments.
Our master analysis script can launch up to 600 GCE single core instances, each running Ubuntu 12.04.
When an instance is launched, we mounted Dex-Net via a persistent disk containing a particular set of objects and grasps.
Each instance pulls our latest code from Github, runs a single python experiment script configured in a YAML file, compresses the results in an output directory, and uploads the results to GCS.
After all instances complete, the master script turns off all instances, unmounts all disks, downloads the results from each instance, and sends the user a notification email.
The results can be optionally analyzed by the master script.

@@

~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
The plot compares Algorithm~\ref{alg:full} with no prior data to uncorrelated Thompson sampling and uniform allocation, two methods used by Laskey et al.~\cite{laskey2015bandits}.
We see that the CCBP model outperforms the uncorrelated model by approximately 10$\times$ for the cereal box but has comparable performance to Thompson sampling on the flower pot.
Iniitial reuslts suggest that performance on the flower pot is poorer because few grasps are similar according to our feature representation.

%Preliminary experiments suggest that using CCBPs with prior data from DexNet reduces the number of samples for MAB algorithms to converge to a grasp with high probablity of force closure $P_F$ under uncertainty in object pose, gripper pose, and friction coefficient.

\begin{figure}[t!]
\centering
	\begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.08]{figures/box_avg_reward_w_model.jpg}
        \caption{Normalized $P_F$ on a cereal box with 250 candidate parallel-jaw grasps.}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.08]{figures/flowerpot_avg_reward_w_model.jpg}
        \caption{Normalized $P_F$ on a flower pot with 250 candidate parallel-jaw  grasps.}
    \end{subfigure}
\caption{Comparison of the normalized $P_F$ of the sampled parallel-jaw grasp versus iteration of the MAB algorithm for correlated Thompson sampling, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials. (a) On the cereal box, correlated Thompson sampling converges to within 90\% of the highest quality grasp approximately 4$\times$ faster than uncorrelated. (b) However, correlated and uncorrelated Thompson sampling perform comparably on the flower pot because there are few grasp similarities in the candidate set. }
\figlabel{local-mab}
\vspace*{-15pt}
\end{figure}

To examine the effects of orders of magnitude of prior data in the MAB algorithms, we ran the algorithms with priors computed from increasingly larger subsets of prior data from Dex-Net: 0, 15, 150, and 1500 objects. 
\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for a bottle and detergent averaged over 50 trials.
For each run of our algorithm, we used prior grasp from the five closest objects in Dex-Net in the multi-view CNN-based shape similiarity vector space.
The objects from Dex-Net were labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
For the bottle, we see that the convergence of the correlated MAB algorithms to a grasp with high $P_F$ accelerates with increasingly larger subsets of prior data used, and is approximately $10 \times$ faster when using 1500 prior objects.
For the detergent the gains are more modest, with the largest dataset accelerating convergence to within 90\% of the optimal grasp in the set by approximately $1.5 \times$.
As illustrated in \figref{bottle-nn}, the nearest neighbor objects become increasingly similar to the object to label with increasing sizes of datasets from Dex-Net.
This suggests that more prior data may also lead to more similar objects to rarer categories such as the detergent bottle, which may accelerate convergence 
\TODO{Remove}
Future work will examine these effects on a larger subset of objects and will use assitional nearest neighbors from Dex-Net to compute priors.

\begin{figure}[t!]
\centering
\begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.08]{figures/bottle_avg_reward_w_model2.jpg}
        \caption{Normalized $P_F$ on a bottle with 250 candidate parallel-jaw grasps.}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[scale=0.08]{figures/detergent_avg_reward_w_model.jpg}
        \caption{Normalized $P_F$ on a detergent bottle with 250 candidate parallel-jaw grasps.}
    \end{subfigure}
%\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model2.jpg}
\caption{Comparison of the normalized $P_F$ of the sampled parallel-jaw grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from Dex-Net, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20. Prior grasps were taken from increasingly larger subsets of Dex-Net: 15, 150, and 1500 objects. For the bottle, convergence to within 90\% of the optimal grasp is accelerated by approximately 10$\times$ over uncorrelated Thompson sampling, and performance appears to improve with increasing sizes of the prior dataset used. The detergent converges slightly faster with more prior data, however the speedup is approximately $1.5\times$ and does not appear to improve with additional data from Dex-Net.}
\figlabel{global-mab}
\vspace*{-15pt}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[scale=0.075]{figures/bottle_nearest_neighbors.jpg}
\caption{Illustration of the five nearest neighbor objects from Dex-Net using the multi-view CNN-based shape embedding and Euclidean distance for increasing sizes of randomly selected subsets of data from Dex-Net. We see that while the neighbors for a small dataset are not relevant, the neighbors become increasingly similar to the query bottle as more data is used.}
\figlabel{bottle-nn}
\vspace*{-15pt}
\end{figure}

@@

\TODO{Write section}

### 2015-09-03 ICRA2016/bandits_docs/includes/introduction.tex
First full version of the paper with committed adobe illustrator figures

\section{Introduction}
Robots in warehousing and small- to medium-scale manufacturing must be able to efficiently handle to new products and parts.
For example, a robot processing orders in a distribution warehouse must be able to quickly adapt to new consumer products to place them in shipping containers.
Analytic methods for grasp planning requires precise knowledge of contact locations and surface normals,
but a robot in the field may not measure these quantities exactly due to sensor imprecision and missing data resulting from occlusions or highly reflective surfaces.
This motivates a fast and adaptive approach to grasp planning that is robust to uncertainty about the state of the robot and environment.

\TODO{I think the parts about force closure should be greatly compressed here}
Force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}, is a commonly-used binary metric of grasp quality.
Past work has measured the probability of force closure given uncertainty in robot state~\cite{brook2011collaborative, hsiao2011bayesian}, object pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose}, and object shape~\cite{brook2011collaborative, hsiao2011bayesian, kehoe2012estimating, mahler2015gp}.
Computing the probability of force closure requires integrating over the uncertain quantities, which many works have computed using computationally expensive Monte-Carlo integration over sampled perturbations~\cite{christopoulos2007handling, hsiao2011bayesian, kehoe2012toward, kim2012physically, weisz2012pose} parallelized in the cloud~\cite{kehoe2012toward} or using iterative pruning of grasps with low quality~\cite{kehoe2012estimating, kehoe2015survey}.

Recently, Laskey et al.~\cite{laskey2015bandits} showed that it was possible to jointly compute the integral and identify the best grasp using Multi-Armed Bandit (MAB) algorithms such as Thompson Sampling, leading to $5-10\times$ speedups over previous work on a set of parallel-jaw grasps on 2D objects.
However, the MAB algorithms still needed roughly 5,000 samples to identify the best grasp from a pool of 1,000 candidates for each object, which could be time-consuming for 3D objects.
Also, the number of samples is prohibitively high to use the algorithms based on physical success from robot trials instead of in simulation.
One possible reason for the magnitude of samples is that this work treated each grasp and object independently, when in reality grasps and objects with similar features, such as those illustrated in\figref{teaser}, should convey information about the probability of success of one another.

\TODO{Need to get correct terminology. Technically not contextual or combinatorial. Ask Kevin.}
Correlated Multi-Armed Bandits (CMABs) are an extension of standard MABs in which options have correlated rewards.
On each observation, standard MAB algorithms update only the predictive model for the option chosen, while CMAB algorithms typically update a global predictive model of the reward for each option.
This can lead to faster convergence if the algorithm has some knowledge of the correlation structure between options.~\cite{}.
A primary challenge is thus estimating a model of the global correlation structure of the arms, which may require a large amount of data.

In this work, we leverage CMABs to accelerate identification of robust grasps using a correlation structure learned from large amounts of data.
We model the probability of force closure for grasps on 3D shapes as a Correlated Continuous Beta Processes (CCBPs)~\cite{}, a model of 0-1 correlated options with computationally inexpensive posterior updates compared to alternative models such as Gaussian Processes~\cite{}.
Each option corresponds to a single grasp center and axis.
Evaluating an option corresponds to sampling from Gaussian uncertainty in object pose, gripper pose, and contact friction, and measuring force closure for the grasp on the sampled state.
We learn the correlation structure between grasps \TODO{Write up}

Our primary contribution is \TODO{Write up}.
Our experiments show that \TODO{Write up}.

>>>>

\section{Introduction}
\seclabel{introduction}

Consider a robot fulfilling orders in a warehouse.
The robot must quickly plan grasps for consumer products to fullfill orders.
Furthermore, the robot may not precisely know the state of the environment, such as the pose or frictional properties of object, due to sensor imprecision and missing data (e.g. occlusions in point clouds).
This poses a challenge for many existing grasp planning methods that are based on precise knowledge of contact locations and surface normals~\cite{ciocarlie2009, ferrari1992} due to the distribution on possible environment configurations.

In vision and speech, advances in Big Data and distributed computing, combined with datasets of milliions of examples such as ImageNet~\cite{deng2009imagenet} and the Fisher corpus~\cite{cieri2004fisher}, have produced impressive results~\cite{hannun2014deepspeech, hays2008im2gps, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
This raises the question: will machine learning of grasps for vast numbers of possible object poses, object shapes, environment configurations, etc., exhibit scaling effects similar to those observed in computer vision and speech recognition?

\begin{figure}[t!]
\centering
\includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
\caption{Sample of 3D mesh models from the Dex-Net dataset. The dataset currently includes over 10,000 models from laser-scanned datsets such as the KIT object database~\cite{kasper2012kit} and the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, and synthetic datasets such as 3DNet\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison}. }
\figlabel{dexnet-teaser}
\vspace*{-15pt}
\end{figure}

We introduce Dex-Net 1.0, a dataset of 3D models and grasps with similarity metrics, and a system for actively acquiring statistical models of grasp quality across the network.
The Dex-Net dataset contains representative 3D models of objects that could be encountered in warehousing or the home.
Dex-Net contains laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} to reflect physical objects commonly used for benchmarking in grasping research.
The dataset also includes synthetic 3D mesh models from shape classification datasets such as 3DNet~\cite{wohlkinger20123dnet}, ModelNet~\cite{wu20143d}, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison} to scale the number of models.
~\figref{dexnet-teaser} shows a sample of the objects in the dataset.
We measure object similarity based the distance between feature vectors generated from multi-view Convolutional Neural Networks (CNNs)~\cite{su2015multi}, a state-of-the are method in shape retrieval
We measure similarity between grasps by the pose of the gripper and local surface ``heightmaps" extracted at location of contact with an object~\cite{herzog2012template, kappler2015leveraging}.
Our system uses Google Cloud Platform to distribute grasp quality evaluations across hundreds of virtual machines and to store millions of grasps across the objects in Dex-Net.

In this work, we use Dex-Net to study the convergence rate of Multi-Armed Bandit (MAB) algorithms for finding a grasp with high probability of force closure under object pose, gripper pose, and friction coefficient uncertainty from a set of 250 candidate grasps on objects from Dex-Net.
To do so, we extend the MAB framework of Laskey et al.~\cite{laskey2015bandits} to model correlations between the probability of force closure for similar grasps on similar 3D objects using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}.
CCBPs predict a belief distribution for the quality of each grasp based similarity to data in Dex-Net that can be efficiently updated after observing the quality of a grasp for a sampled object pose, gripper pose, and friction coefficient.
Our results suggest that CCBPs bootstrapped with data from Dex-Net can accelerate grasp planning by up to $10\times$.

### 2015-09-03 ICRA2016/bandits_docs/includes/problem_statement.tex
First full version of the paper with committed adobe illustrator figures

We consider the problem of finding the parallel-jaw grasp with the maximum probability of a binary success metricsuch as force closure on a previously unknown object under uncertainty in object pose, gripper pose, and friction coefficient.

\subsection{Grasp and Object Model}
Our grasping model is illustrated in~\figref{grasp-model}.
Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \mS^2$.
We assume that the gripper will be opened to its maximal width before closing on the object.
Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{newcombe2011kinectfusion, mahler2015gp}, which is zero on the object surface, positive outside the object, and zero inside the object. 
We assume that the object is specified in units of meters and the object center of mass $\bz \in \mathbb{R}^3$ is known.
Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3, \bv \in \mS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where $\mF$ is the space of all SDFs.
Our joint grasp and object space, or Grasp Moduli Space~\cite{pokorny2013grasp}, is $\mM = \mG \times \mH$.

@@

\subsection{Contact Model}
Our contact model is illustrated in the right panel of \figref{grasp-model}.
Given object shape and samples of object pose, and gripper pose, we let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
Furthermore, let $\bn_i \in \mS^2$ denote the surface normal at contact $\bc_i$.
To compute the forces that each contact can apply to the object, we discretize the friction cone at contact $i$ into a discrete set of $N_c$ facets with vertices $\bbf_{i,j}$ for $j = 1, ..., N_c$~\cite{pokorny2013classical} for a given friction coefficient $\gamma$.
Each force $\bbf_{i,j}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
Thus the set of all wrenches that can be applied by a grasp $\bg$ is $\mW = \{ \bw_{i,j} = [\bbf_{i,j}, \tau_{i,j}]^T \big| i = 1, 2 \text{ and } j = 1, ..., N_c\}$.

\subsection{Quality Metric}
In this work we use force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
We acknowledge that force closure assumes the abliity to actuate the gripper to apply arbitrary forces in the contact friction cone~\cite{} and that some evidence suggests that deterministic force closure is not a strong predictor of physical grasp success~\cite{balasubramanian2012physical}.
However, we use the probability of force closure because of it has shown some promise in physical experiments~\cite{kim2012physically, weisz2012pose}, and it is relatively inexpensive to evaluate as compared to human labels or physical executions, allowing us to better study the effects of large amounts of data on convergence.

Let $F \in \{0, 1\}$ denote the occurence of force clsoure.
To compute force closure for a grasp $\bg$ on object $\mO$ given deterministic samples of object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$, we first compute the set of possible contact wrenches $\mW$.
Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$.
A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.

@@

\subsection{Objective}
The probability of force closure for a grasp $\bg$ is
%\vspace{-2ex}
\begin{align*}
	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \rho, \zeta \right).
\end{align*}
\noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$:

@@

As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ where $\Gamma$ is set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
However, even with a discrete set of candidates, fully evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
Thus, past work has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.

\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent under uncertainty}

>>>>

Given a previously unknown object, we consider the problem of finding the parallel-jaw grasp with the maximum expected grasp quality according to a binary grasp quality metric such as force closure under uncertainty in object pose, gripper pose, and friction coefficient.

\subsection{Grasp and Object Model}
Our grasping model is illustrated in~\figref{grasp-model}.
Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
We assume that the jaws are opened to their maximal width $w \in\bR$ before closing on the object.
Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}, which is zero on the object surface, positive outside the object, and zero inside the object. 
We assume that the object is specified in units of meters and the object center of mass $\bz \in \mathbb{R}^3$ is known.
Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where $\mF$ is the space of all SDFs.
Our joint space of grasps and objects, or Grasp Moduli Space~\cite{pokorny2013grasp}, is $\mM = \mG \times \mH$.

@@

\subsection{Contact Model}
\seclabel{contact}
Our contact model is illustrated in the right panel of \figref{grasp-model}.
Given a grasp $\bg$ with width $w$ on an object $\mO$ and samples of object pose, gripper pose, and friction, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
We can compute the contacts using
\begin{align*}
	\bc_1 &= \minimum{t \geq 0} t \text{ such that } | f\left(\bx + (t - w / 2) \bv\right) | < \epsilon \\
	\bc_2 &= \minimum{t \geq 0} t \text{ such that } | f\left(\bx - (t - w / 2) \bv\right) | < \epsilon
\end{align*}
\noindent where $\epsilon > 0$ is a user-specified surface resolution~\cite{mahler2015gp}.

Given contact points, let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tanget vectors $\bt_{i,1}, \bt_{i,2} \in \mS^2$.
To compute the forces that each contact can apply to the object for a given friction coefficient $\gamma$, we discretize the friction cone at contact $i$ into a discrete set of $l$ facets with vertices $\mF_{i} = \left\{ \bbf_{i,j} = \bn_i + \gamma \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \gamma \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \text{ for } j = 1, ..., l \right\}$~\cite{pokorny2013classical}.
Each force $\bbf_{i,j}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
To enable force closure with two contacts in 3D we assume a soft contact model, under which each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = [\mathbf{0}, \bn_i]^T$~\cite{prattichizzo2008grasping}.
Thus the set of all wrenches that can be applied by a grasp $\bg$ under our model is $\mW = \{ \bw_{i,j} = [\bbf_{i,j}, \tau_{i,j}]^T \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.

\subsection{Quality Metric}
\seclabel{quality}
In this work we use force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
We acknowledge that force closure assumes the abliity to actuate the gripper to apply arbitrary forces in the contact friction cone~\cite{}, and that some evidence suggests that deterministic force closure is not always a strong predictor of physical grasp success~\cite{balasubramanian2012physical}.
However, we use the probability of force closure because of it has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose}, and it is relatively inexpensive to evaluate when compared to human labels or physical executions, allowing us to better study the effects of large amounts of data.

Let $F \in \{0, 1\}$ denote the occurence of force closure.
To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$, we first compute the set of possible contact wrenches $\mW$.
Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$~\cite{weisz2012pose}.
A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.

@@

\subsection{Objective}
The probability of force closure for a grasp $\bg$ on object $\mO$ is
%\vspace{-2ex}
\begin{align*}
	P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right).
\end{align*}
\noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
To perform this as quickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$~\cite{laskey2015bandits}:

@@

As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ where $\Gamma$ is set by sampling grasp centers from a Gaussian with mean at the object center~\cite{laskey2015bandits} or using heuristics specific to parallel-jaw grippers such as antipodality~\cite{mahler2015gp}.
However, even with a discrete set of candidates, fully evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
Thus, past research has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit (MAB) algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
In this work, we extend the MAB model of~\cite{laskey2015bandits} to model similarities between grasps and prior objects in Dex-Net to further accelerate convergence.

%\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent under uncertainty}
